Predictors of frog survival following translocations - create dataset

### 2022-03-16 code/translocation_survival_createdata.Rmd
Add snow_wc variable to translocation dataset

```{r create-day-year}
frog_translocation <- frog_translocation %>% 
  mutate(day = yday(release_date),
         year = year(release_date))
```

@@

```{r final-translocation-dataset}
frog_translocation <- frog_translocation %>% 
  rename(survival = median_survival,
         donor = collect_siteid,
         date = release_date) %>% 
  select(site_id, elevation, shore, date, day, year, order, pit_tag_ref, donor, sex, length, weight, bd_load, survival) 
```

>>>>

```{r add-day-year}
frog_translocation <- frog_translocation %>% 
  mutate(day = yday(release_date),
         year = year(release_date))
```

### Add snowpack data for winter of and winter following translocation

```{r add-snowpack}

source("snowwc_clean.R")

frog_translocation <- snowwc_dan %>% 
  mutate(year_t = year, 
         year_t1 = (year + 1)) %>% 
  rename(snow_t = snowwc_cm) %>% 
  select(year, year_t, year_t1, snow_t) %>% 
  inner_join(snowwc_dan, by = c("year_t1" = "year")) %>% 
  rename(snow_t1 = snowwc_cm) %>% 
  select(-station_id, -date, -snowwc_pave) %>% 
  inner_join(frog_translocation, by = "year")
```

@@

```{r final-translocation-dataset}
frog_translocation <- frog_translocation %>% 
  rename(survival = median_survival,
         donor = collect_siteid,
         date = release_date) %>% 
  select(site_id, elevation, shore, snow_t, snow_t1, date, year, day, order, pit_tag_ref, donor, sex, length, weight, bd_load, survival) 
```
